\bf Swinging, Fast and Slow: Interpreting Variation in Baseball Swing Tracking Metrics

### 2025-07-14 articles/tas/paper.tex
final touches for TAS submission

\newcommand{\anon}{0}

@@

\if1\anon
{
  \title{\bf Swinging, Fast and Slow: Interpreting Variation in Baseball Swing Tracking Metrics}
  \author{Scott Powers \\
    Department of Sport Management, Rice University \\
    and \\
    Ronald Yurko \\
    Department of Statistics \& Data Science, Carnegie Mellon University
  }
  \maketitle
} \fi

@@

        \begin{table}
          \hspace{-6mm}
          \begin{tabular}{cl|rrrr}
                  &                                             & \multicolumn{4}{c}{XGBoost Hyperparameters}\\
            Model & Description                                 & \texttt{nrounds}  & \texttt{eta}        & \texttt{max\_depth} & \texttt{min\_child\_weight}\\
            \hline        
                  & Hit outcome model                           & 1000              & 0.05                & 9                   & 100\\
            \hline        
                  & {\it Pitch outcome model}\\
            \{A\} & Probability of swing                        & 1500              & 0.05                & 9                   & 10\\
            \{B\} & Probability of HBP given no swing  &  400              & 0.05                & 6                   & 10\\
            \{C\} & Probability of contact given swing          & 1000              & 0.01                & 6                   & 100\\
            \{D\} & Probability of strike given called pitch    & 2000              & 0.01                & 9                   & 10\\
            \{E\} & Probability of fair ball given contact      & 1500              & 0.01                & 9                   & 100\\
            \{F\} & Expected xLW given fair ball                & 1000              & 0.01                & 6                   & 100\\
            \hline
                & Hyperparameter search space                   & (0, 2000]         & \{0.01, 0.05, 0.3\} & \{3, 6, 9\}         & \{10, 30, 100\}
          \end{tabular}
          \caption{\it Descriptions and hyperparameters for hit outcome model and pitch outcome model components. Gradient boosting hyperparameters were tuned using 5-fold cross-validation, except for \texttt{gamma} (0), \texttt{subsample} (0.65), and \texttt{colsample\_by\_tree} (0.7), which were fixed in advance.}
          \label{tab:xgboost-hyperparameters}
        \end{table}

@@

@@

  \section*{Code Availability}

    All code related to this paper is available at \url{https://github.com/saberpowers/swinging-fast-and-slow}.

  \section{Data Availability Statement}\label{data-availability-statement}

    Deidentified data have been made available at the following URL: XX.

@@

  \begin{itemize}
  \tightlist
  \item
    If you have supplementary material (e.g., software, data, technical
    proofs), identify them in the section below. In early stages of the
    submission process, you may be unsure what to include as supplementary
    material. Don't worry---this is something that can be worked out at
    later stages.
  \end{itemize}

  \phantomsection\label{supplementary-material}
  \bigskip

  \begin{center}

  {\large\bf SUPPLEMENTARY MATERIAL}

  \end{center}

  \begin{description}
  \item[Title:]
  Brief description. (file type)
  \item[R-package for MYNEW routine:]
  R-package MYNEW containing code to perform the diagnostic methods
  described in the article. The package also contains all datasets used as
  examples in the article. (GNU zipped tar file)
  \item[HIV data set:]
  Data set used in the illustration of MYNEW method in
  Section~\ref{sec-verify} (.txt file).
  \end{description}

>>>>

\newcommand{\anon}{1}

@@

\if1\anon
{
  \title{\bf Swinging, Fast and Slow: Interpreting Variation in Baseball Swing Tracking Metrics}
  \author{Scott Powers\thanks{Both authors contributed equally to this work.} \\
    Department of Sport Management, Rice University \\
    and \\
    Ronald Yurko$^{\footnotesize *}$ \\
    Department of Statistics \& Data Science, Carnegie Mellon University
  }
  \maketitle
} \fi

@@

        \begin{table}
          \footnotesize
          \hspace{-6mm}
          \begin{tabular}{cl|rrrr}
                  &                                             & \multicolumn{4}{c}{XGBoost Hyperparameters}\\
            Model & Description                                 & \texttt{nrounds}  & \texttt{eta}        & \texttt{max\_depth} & \texttt{min\_child\_weight}\\
            \hline        
                  & Hit outcome model                           & 1000              & 0.05                & 9                   & 100\\
            \hline        
                  & {\it Pitch outcome model}\\
            \{A\} & Probability of swing                        & 1500              & 0.05                & 9                   & 10\\
            \{B\} & Probability of HBP given no swing  &  400              & 0.05                & 6                   & 10\\
            \{C\} & Probability of contact given swing          & 1000              & 0.01                & 6                   & 100\\
            \{D\} & Probability of strike given called pitch    & 2000              & 0.01                & 9                   & 10\\
            \{E\} & Probability of fair ball given contact      & 1500              & 0.01                & 9                   & 100\\
            \{F\} & Expected xLW given fair ball                & 1000              & 0.01                & 6                   & 100\\
            \hline
                & Hyperparameter search space                   & (0, 2000]         & \{0.01, 0.05, 0.3\} & \{3, 6, 9\}         & \{10, 30, 100\}
          \end{tabular}
          \caption{\it Descriptions and hyperparameters for hit outcome model and pitch outcome model components. Gradient boosting hyperparameters were tuned using 5-fold cross-validation, except for \texttt{gamma} (0), \texttt{subsample} (0.65), and \texttt{colsample\_by\_tree} (0.7), which were fixed in advance.}
          \label{tab:xgboost-hyperparameters}
        \end{table}

@@

  \subsection*{Acknowledgments}

    The authors thank Noah Woodward and Nick Wan for early stage discussions and feedback on this work.

@@

  \section*{Data Availability Statement}

    Data and models have been made available at the following URL: \url{https://doi.org/10.25611/7QXV-8612}. All code is available at \url{https://github.com/saberpowers/swinging-fast-and-slow}.

@@
